Transcriptomic Analysis for Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-07-04 Cover_letter_JPM.tex
Updates from Overleaf

@@

% mark in blue or red
\usepackage{xcolor}
%\usepackage[table,xcdraw]{xcolor}
\newenvironment{MyColorPar}[1]{%
    \leavevmode\color{#1}\ignorespaces%
}{%
}%

@@

% modify on main.tex, marked with
%\begin{MyColorPar}{red}
%\end{MyColorPar}
% from page (ok)
The summary of holistic cancer care in this revised manuscript could be on the paragraphs marked in \textcolor{red}{Red} on page 13 (line 377 to line 392). Also, it is shown here in the following paragraph.

@@

\textcolor{blue}{In the section of Results}\\
"
TCGA HNSCC cohort was applied for exploration of the biomarker candidate.
A total of 9416 Kaplan-Meier plots (under sliding-window cutoff selection) with associated Cox's univariate and multivariate tables were generated by Cox modeling (see Figure ~\ref{fig:figure1}) and justified by the ranking of hazard ratios.
%The ten genes, named DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, 
The 967 out of 9416 genes were kept by criteria of Kaplan-Meier \textit{P} value ($< 0.05$) and \acrfull{hr} derived from Cox's model (please see Figure 2(a), (b), initial trial).
In the next step, a Bonferroni P-value correction was used to yield 20 genes, under the stringent criteria (see Figure 2(c), (d)).
%em dash ---
These CAMK2N1, CALML5, FCGBP and the other 17 genes (DKK1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, ZNF557, ZNF266, MYO1H, LOC148709, EVPLL, PNMA5, IQCN---previous name as KIAA1683, and NPB) have significant FDR-adjusted \textit{P} values ($< 0.0003$) in Kaplan-Meier estimate, and greater hazard ratio (HR) ($> 1.8$ or $< 0.6$) in Cox's model (please see Figure \ref{fig:hazards3}; $log_{10}(0.0003) = -3.5$).
%These genes have also passed a stringent criteria (Bonferroni \textit{P} value correction less than 0.05).
The plot reveals that the top 20 genes (Bonferroni-adjusted \textit{P} $< 0.05$) are located on the peaks. At the same time, Cox's HR separates them on the two-side with significant prognostic impact.
%During our exploration phase with TCGA cohort, the 20 genes, listed
%six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
%four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are good guy.
%}
%in Figure \ref{fig:hazards3}, have FDR-adjusted \textit{P} values ($<0.001$) in Kaplan-Meier estimate, and survival impact on HR ($> 1.8$ or $< 0.6$) in Cox's model.

@@

\begin{figure}[!tbp]
%     % two PDF side by side \usepackage{subcaption}
  \begin{subfigure}[b]{0.5\textwidth}
        \includegraphics[width=\textwidth]{Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf}
        \caption{TCGA HNSCC cohort}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.5\textwidth}
       \includegraphics[width=\textwidth]{Rplot_GSE65858_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf} 
       \caption{GSE65858 HNSCC cohort}
  \end{subfigure}
  \caption{The 62 genes (listed on the right) have been discovered by LASSO regression in (a) TCGA HNSCC and (b) GSE65858 HNSCC cohort. \textcolor{red}{Red}-square marked genes are our 3 candidates.}
  \label{fig:Bayes62}
\end{figure}

@@

%
\begin{MyColorPar}{blue}
Answer
%(OK x3)
% (ok) minor comments1
We appreciate the reviewer for the critical comments and thanks for the agreement of our workflow in cancer research.
The description of the linear model has been removed. 
Detailed introduction of TCGA-related tools has been moved to the Materials and Methods.
We made a new Figure 1 with clear direction of the workflow.
A "gene expression values (20500 genes)" in Figure 1, instead of "RNAseq", indicates the expression data obtained from the TCGA.
In Figure 2, the ticks and labels on the x-axis were corrected.\\[0.5cm]

@@

\begin{outline} % highlight still blue
In conclusion, 20 candidate biomarkers, DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, as well as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (former name as KIAA1683), and NPB, are associated with the prognosis of OS in our study.
Comparison with previous publications or database analyses,

>>>>

%\usepackage{xr}  % for cross-reference
\usepackage{xr-hyper}
\usepackage{hyperref}

%\newcommand{\R}[1]{\label{#1}\linelabel{#1}} % for \label page and line
%\newcommand{\lr}[1]{page~\pageref{#1} (line~\lineref{#1})} % for \ref page and line
\makeatletter
  \long\def\myempty{}
  \def\XR@addURL#1{\XR@@dURL#1\myempty{}{}{}{}{}\\}
  \def\XR@@dURL#1#2#3#4#5#6#7\\{%
    {#1}{#2}%
    \ifx\myempty#6\@empty
      {#3}{#4}{\XR@URL}%
    \else
    \fi
  }
\makeatother

\makeatletter
\newcommand*{\addFileDependency}[1]{% argument=file name and extension
  \typeout{(#1)}
  \@addtofilelist{#1}
  \IfFileExists{#1}{}{\typeout{No file #1.}}
}
\makeatother

\newcommand*{\myexternaldocument}[1]{%
    \externaldocument{#1}%
    \addFileDependency{#1.tex}%
    \addFileDependency{#1.aux}%
}
% turn it off
%\myexternaldocument{main} % or main_REDmarked_revision2.tex
%\externaldocument{main}

@@

% mark in blue or red
\usepackage{xcolor}
\definecolor{asparagus}{rgb}{0.53, 0.66, 0.42}
%\usepackage[table,xcdraw]{xcolor}
\newenvironment{MyColorPar}[1]{%
    \leavevmode\color{#1}\ignorespaces%
}{%
}%

@@

% modify on main.tex, marked with
%\begin{MyColorPar}{red}
%\end{MyColorPar}
% from page (ok)
% Please see page 3, line 23. begins on line 1, page 3, to line 2, page 4.
The summary of holistic cancer care in this revised manuscript could be on the paragraphs marked in \textcolor{red}{Red} on page 13 (line 377 to 392).
%and on page \pageref{from:answer1-2}, line?
%\lr{to:answer1-2}. \lineref[1]{to:answer1-2}),
% \lr{from:answer1-2}
%(line 377 \ref{line_fr:answer1-2}) to page \pageref{page_to:answer1-2} (line 392 \ref{line_to:answer1-2}). 
%\pagelabel{from:answer1-2} \linelabel{from:answer1-2L}
Also, it is shown here in the following paragraph.
% line \ref{line_fr:answer1-2} ~ \ref{line_to:answer1-2} of page %\pageref{page_fr:answer1-2}, \pageref{page_to:answer1-2}
% in main.tex
% %\label{page_fr:answer1-2}, \label{page_to:answer1-2}
% \linelabel{line_fr:answer1-2} , \linelabel{line_to:answer1-2}

@@

\textcolor{blue}{In the section of Results}\\
"
TCGA HNSCC cohort was applied for exploration of the biomarker candidate.
A total of 9416 Kaplan-Meier plots (under sliding-window cutoff selection) with associated Cox's univariate and multivariate tables were generated by Cox modeling (see Figure \ref{fig:figure1}) and justified by the ranking of hazard ratios.
%The ten genes, named DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, 
The 967 out of 9416 genes were kept by criteria of Kaplan-Meier \textit{P} value ($< 0.05$) and \acrfull{hr} derived from Cox's model (please see Figure 2(a), (b), initial trial).
In the next step, a Bonferroni P-value correction was used to yield 20 genes, under the stringent criteria (see Figure 2(c), (d)).
%em dash ---
These CAMK2N1, CALML5, FCGBP and the other 17 genes (DKK1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, ZNF557, ZNF266, MYO1H, EVPLL, PNMA5, IQCN, NPB, and CALML5) have significant FDR-adjusted \textit{P} values ($< 0.0003$) in Kaplan-Meier estimate, and greater hazard ratio (HR) ($> 1.8$ or $< 0.6$) in Cox's model (please see Figure \ref{fig:hazards3}; $log_{10}(0.0003) = -3.5$).
%These genes have also passed a stringent criteria (Bonferroni \textit{P} value correction less than 0.05).
The plot reveals that the top 20 genes (Bonferroni-adjusted \textit{P} $< 0.05$) are located on the peaks. At the same time, Cox's HR separates them on the two-side with significant prognostic impact.
%During our exploration phase with TCGA cohort, the 20 genes, listed
%six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
%four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are good guy.
%}
%in Figure \ref{fig:hazards3}, have FDR-adjusted \textit{P} values ($<0.001$) in Kaplan-Meier estimate, and survival impact on HR ($> 1.8$ or $< 0.6$) in Cox's model.

@@

\begin{figure}[!tbp]
%     % two PDF side by side \usepackage{subcaption}
  \begin{subfigure}[b]{0.5\textwidth}
        \includegraphics[width=\textwidth]{Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf}
        \caption{TCGA HNSCC cohort}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.5\textwidth}
       \includegraphics[width=\textwidth]{Rplot_GSE65858_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf} 
       \caption{GSE65858 HNSCC cohort}
  \end{subfigure}
  \caption{The 62 genes (listed on the right), discovered by LASSO regression, distribute in (a) TCGA HNSCC and (b) GSE65858 HNSCC cohorts. \textcolor{red}{Red}-square marked genes are our 3 candidates: CAMK2N1, CALML5, and FCGBP.}
  \label{fig:Bayes62}
\end{figure}

@@

%(OK x3)
% (ok) minor comments1
We appreciate the reviewer for the critical comments and thanks for the agreement of our workflow in cancer research.
The description of the linear model has been removed. 
Detailed introduction of TCGA-related tools has been moved to the Materials and Methods.
We made a new "Figure 1" with clear direction of the workflow.
And the "gene expression values (20500 genes)" replaced the "RNAseq" (it is shown here as Figure \ref{fig:figure1} on page \pageref{page21}).
In "Figure 2", the ticks and labels on the x-axis were corrected (please also see Figure \ref{fig:figure2} on page \pageref{page22} in this file).\\[0.5cm]

%%% new figure 1; fig:figure1

%\subsubsection{Figure 1:h}
\begin{figure}[hbt!]
\centering
%\widefigure
\includegraphics[width=14cm]{Figure_1_manuscript_workflow} % .PDF is better than .png
%, height=8cm
%\caption % , step 1 (\textcolor{blue}{blue line}: main procedure) and step 2 (\textcolor{orange}{orange line}: analysis export).
%Step 3 (purple line: dealing with surgical margin).
\bcaption{A workflow of \acrshort{hnscc} biomarker discovery}
{The workflow includes data retrieval from TCGA GDC data portal, data process with merging and cleaning, then performing the survival analyses (within \textcolor{yellow}{yellow} square). The Cutoff engine (in R script: cutofFinder\_func.HNSCC.R, a serial cut for grouping patients with \textcolor{asparagus}{low} or \textcolor{red}{high} expression of a specific gene, to yield a collection of \textit{P} values; please see Materials and Methods section for details) might calculate all possible Kaplan-Meier \textit{P} values (corrected by \acrlong{fdr}, FDR, method) to find the optimal cutoff value of gene expression for subsequent Cox modeling.
The candidate selection performs (1) dissecting and selection of candidate genes by further Bonferroni adjusted \textit{P} values as well as a hazard ratio of Cox model, based on the results from the survival analyses;
(2) survival analyses of the other HNSCC dataset (GSE65858) using Kaplan-Meier estimate (with FDR correction) and Cox modeling.\\
The biomarker candidates were a consensus result of TCGA and GSE65858. 
%The selected genes were validated by third HNSCC cohort (GSE2837).\\
(HNSCC: head and neck squamous cell carcinoma; TCGA: the Cancer Genome Atlas; RNA-Seq: RNA sequencing; GDC: Genomic Data Commons.)}
\label{fig:figure1}
% Description:1) FDR correction of Kaplan-Meier \textit{P} values during Cutoff finding; and 2) Bonferroni correction of Kaplan-Meier \textit{P} values after Cox modeling for candidate selection.

\label{page21}
\end{figure}

%%% new figure 2; fig:figure2

%\subsubsection{Figure 2:h}
\begin{figure}[hbt!]
\centering
\includegraphics[width=14cm]{Figure2.pdf}
\bcaption{The initial progress of candidate selection from TCGA \acrshort{hnscc} cohort.}{The \textit{P} values of Kaplan-Meier survival is one of the selection criteria.
The effect size is estimated by Cox's hazard ratio.
Initial trial step: (a) univariate HR versus \textit{P} value; (b) multivariate HR versus \textit{P} value.
After stringent criteria by Bonferroni-adjusted \textit{P} value, and the Cox's HR, few top-ranked genes are shown in
(c) univariate HR versus Bonferroni-adjusted \textit{P} value; and (d) multivariate HR versus Bonferroni-adjusted \textit{P} value.\\
(TCGA: \acrlong{tcga}; HR: hazard ratio)}
\label{fig:figure2}
\label{page22}
\end{figure}

@@

%LOC148709
\begin{outline} % highlight still blue
In conclusion, 20 candidate biomarkers, DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, as well as ZNF557, ZNF266, IL19, MYO1H, FCGBP, EVPLL, PNMA5, IQCN, NPB and CALML5, are associated with the prognosis of OS in our study.
Comparison with previous publications or database analyses,

### 2021-07-04 Supplementary_figures.tex
Updates from Overleaf

% Supplementary_figures.tex
%\documentclass[preprint,12pt]{elsarticle}
\documentclass[jpm,supfile,submit,moreauthors,pdftex]{Definitions/mdpi}

% major revision and answer question (3 reviewers)
%Sunday, January 24⋅22:30 – 22:55
%Daily, until Jan 29, 2021

@@

\begin{document}
%%%%%%%%% title
% Full title of the paper (Capitalized)
\Title{Transcriptomic Analysis for Prognostic Value in Head and Neck Squamous Cell Carcinoma}\\[2cm]
%x Title: A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma\\[2cm]
%}

%==================

%\underline{Supplementary information}
% title and author

\section{STables}
\underline{Supplementary figure legends}\\[1cm]
%ST1
%Supplementary Table \ref{table:table1}\\
%GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of high risk and low risk groups, which is derived from cumulative P-value plots). The poor prognostic genes are marked as red; the better prognostic genes are marked as green.

%ST2
Supplementary Table \ref{table:table3}\\

@@

CAMK2N1                                        & calcium/calmodulin-dependent protein kinase II inhibitor 1 & \num{2.9e-7}                               & 0.002                                                                           & 2.101                                      & 1.572-2.809                                & 2.007                                      & 1.490-2.704                                & \checkmark                                          \\ 

@@

PGK1                                           & phosphoglycerate kinase 1                                  & \num{9.1e-7}                               & 0.006                                                                           & 2.127                                      & 1.563-2.895                                & 2.046                                      & 1.498-2.795                                & \checkmark                                          \\ 

@@

SURF4                                          & surfeit 4                                                  & \num{9.6e-7}                               & 0.006                                                                           & 2.055                                      & 1.531-2.757                                & 2.089                                      & 1.543-2.829                                & \checkmark                                           \\ 

@@

USP10                                          & ubiquitin specific peptidase 10                            & \num{1.7e-6}                               & 0.012                                                                           & 2.083                                      & 1.532-2.834                                & 2.119                                      & 1.551-2.895                                & \checkmark                                         \\ 

@@

NDFIP1                                         & Nedd4 family interacting protein 1                         & \num{2.6e-6}                               & 0.017                                                                           & 2.031                                      & 1.502-2.746                                & 2.027                                      & 1.483-2.771                                & \checkmark                                           \\ 

@@

FOXA2                                          & forkhead box A2                                            & \num{2.7e-6}                               & 0.018                                                                           & 1.976                                      & 1.479-2.640                                & 1.914                                      & 1.426-2.569                                & \checkmark                                          \\ 

@@

\multicolumn{9}{|l!{\color{black}\vrule}}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~~\\~Kaplan-Meier Bonferroni-adjusted \textit{P} $< 0.05 $~\\~Cox's univariate and multivariate$ HR >= 1.5$ \end{tabular}}                                                                                                                                                                                                                                                              \\ 

@@

\multicolumn{9}{|l!{\color{black}\vrule}}{}%Remark: \checkmark validated by GSE2837}                                                                                                                                                                                                                                                                                                                                                             \\

@@

@@

\caption{The other top 10 genes overexpressed with better prognosis in \acrshort{hnscc} (ranked by corrected \textit{P} value) }

@@

ZNF557                                         & zinc finger protein 557                                & \multicolumn{1}{l!{\color{black}\vrule}}{\textcolor[rgb]{0,0,0.471}{\num{8.6e-8}}} & \multicolumn{1}{l!{\color{black}\vrule}}{0.001}                                                      & \multicolumn{1}{l!{\color{black}\vrule}}{0.465} & \multicolumn{1}{l!{\color{black}\vrule}}{0.348-0.619} & \multicolumn{1}{l!{\color{black}\vrule}}{0.499} & \multicolumn{1}{l!{\color{black}\vrule}}{0.372-0.669} &                                              \\ 

@@

ZNF266                                         & zinc finger protein 266                                & \textcolor[rgb]{0,0,0.471}{\num{2.2e-7}}                                           & 0.001                                                                                                & 0.474                                           & 0.355-0.632                                           & 0.453                                           & 0.338-0.607                                           &                                              \\ 

@@

IL19                                           & interleukin 19                                         & \textcolor[rgb]{0,0,0.471}{}\num{3.7e-7}\textcolor[rgb]{0,0,0.471}{}               & 0.002                                                                                                & 0.472                                           & 0.351-0.635                                           & 0.459                                           & 0.340-0.619                                           & \checkmark                                            \\ 

@@

MYO1H                                          & myosin 1H                                              & \textcolor[rgb]{0,0,0.471}{}\num{3.8e-7}\textcolor[rgb]{0,0,0.471}{}               & 0.003                                                                                                & 0.468                                           & 0.347-0.632                                           & 0.467                                           & 0.344-0.634                                           &                                              \\ 

@@

FCGBP                                          & Fc fragment of IgG binding protein                     & \textcolor[rgb]{0,0,0.471}{}\num{1.2e-6}\textcolor[rgb]{0,0,0.471}{}               & 0.008                                                                                                & 0.484                                           & 0.359-0.653                                           & 0.496                                           & 0.366-0.674                                           &  \checkmark                                           \\ 

@@

LOC148709                                      & LncRNA LOC148709                                       & \textcolor[rgb]{0,0,0.471}{\num{1.5e-6}}                                           & 0.010                                                                                                & 0.499                                           & 0.374-0.666                                           & 0.485                                           & 0.361-0.652                                           &                                              \\ 

@@

EVPLL                                          & envoplakin-like protein                                & \textcolor[rgb]{0,0,0.471}{\num{2.0e-6}}                                           & 0.013                                                                                                & 0.490                                           & 0.363-0.661                                           & 0.494                                           & 0.364-0.672                                           &                                              \\ 

@@

PNMA5                                          & paraneoplastic antigen like 5                          & \textcolor[rgb]{0,0,0.471}{\num{2.6e-6}}                                           & 0.017                                                                                                & 0.499                                           & 0.371-0.671                                           & 0.481                                           & 0.357-0.650                                           &                                              \\ 

@@

KIAA1683                                       & new name as IQ Motif Containing N (IQCN)                           & \textcolor[rgb]{0,0,0.471}{\num{3.1e-6}}                                           & 0.020                                                                                                & 0.500                                           & 0.371-0.673                                           & 0.483                                           & 0.356-0.654                                           &   \checkmark                                           \\ 

@@

NPB                                            & neuropeptide B                                         & \textcolor[rgb]{0,0,0.471}{\num{4.0e-6}}                                           & 0.027                                                                                                & 0.460                                           & 0.328-0.646                                           & 0.457                                           & 0.324-0.646                                           &      \checkmark                                        \\ 

@@

                                               &                                                        &                                                                                    &                                                                                                      &                                                 &                                                       &                                                 &                                                       & \multicolumn{1}{l|}{}                         \\ 
\multicolumn{9}{|l|}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~\\~Kaplan-Meier Bonferroni-adjusted \textit{P} value \textless{} 0.05~\\~Cox's univariate and multivariate HR \textless{}= 1.5\\

@@

lncRNA: Long non-coding RNA\\%Remark: \checkmark Validated by GSE2837

@@

\section{SFigures}
\underline{Supplementary figure legends}\\[1cm]
%S1
Supplementary figure \ref{fig:pvaluePlot_NDFIP1}\\
The gene NDFIP1, one of our 20 preliminary candidates, has a \textit{P} value (around $0.05$) at 50\% quantile cutoff, achieving a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff (please see supplementary Figure S1). After the FDR correction, NDFIP1 still has \textit{P} value of \num[round-precision=3, round-mode=figures,
scientific-notation=true]{0.0001074233}.
However, NDFIP1 could not pass the validation by using GSE65858 cohort.

@@

%%%%%
% S1
% supplementary figure
\begin{figure}[ht]
    \centering
    \includegraphics[width=10cm]{Rplot_pvaluePlot_NDFIP1.pdf}
    \caption{Under cutoff-finding procedure of Kaplan-Meier analysis, the \textit{P}-value plot of gene "NDFIP1" shows: 1) 70\% of \textit{P} values is $<0.05$; 2) the median-cut zone (zoom-in and revealed in inset box) has a "W"-like distribution; 3) sliding-window cutoff selection could find it's optimized \textit{P} values (far less than 0.001) while a median cut might yield \textit{P} value $>=0.05$.\\
    (x-axis: grouping by person number; y-axis: \textit{P} value in log10 transformed)}
    \label{fig:pvaluePlot_NDFIP1}
\end{figure}

@@

%%%
% MDPI internal command: Title for citation in the left column
\TitleCitation{A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma}

>>>>

% Supplementary_figures.tex
%\documentclass[preprint,12pt]{elsarticle}
\documentclass[jpm,supfile,submit,moreauthors,pdftex]{Definitions/mdpi}
%supfile
% major revision and answer question (3 reviewers)
%Sunday, January 24⋅22:30 – 22:55
%Daily, until Jan 29, 2021 => JPM 2021/07/05

@@

%%%%%%%%% title
% Full title of the paper (Capitalized)
\Title{Transcriptomic Analysis for Prognostic Value in Head and Neck Squamous Cell Carcinoma}\\[2cm]
%x Title: A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma\\[2cm]
%}

%==================
\begin{document}
%\underline{Supplementary information}
% title and author

\section{STables}
%\underline{Supplementary figure legends}\\[1cm]
%ST1
%Supplementary Table \ref{table:table1}\\
%GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of high risk and low risk groups, which is derived from cumulative P-value plots). The poor prognostic genes are marked as red; the better prognostic genes are marked as green.

%ST2
Supplementary Table \ref{table:table1}: \\
Overexpression of 10 genes with Cox's hazard ratio $> 1.5$.\\

Supplementary Table \ref{table:table3}: \\
Overexpression of 10 genes with Cox's hazard ratio $< 0.6$. \\

@@

CAMK2N1                                        & calcium/calmodulin-dependent protein kinase II inhibitor 1 & \num{2.9e-7}                               & 0.002                                                                           & 2.101                                      & 1.572-2.809                                & 2.007                                      & 1.490-2.704                                &                                           \\ %\checkmark

@@

PGK1                                           & phosphoglycerate kinase 1                                  & \num{9.1e-7}                               & 0.006                                                                           & 2.127                                      & 1.563-2.895                                & 2.046                                      & 1.498-2.795                                &                                           \\ %\checkmark

@@

SURF4                                          & surfeit 4                                                  & \num{9.6e-7}                               & 0.006                                                                           & 2.055                                      & 1.531-2.757                                & 2.089                                      & 1.543-2.829                                &                                          \\ %\checkmark  

@@

USP10                                          & ubiquitin specific peptidase 10                            & \num{1.7e-6}                               & 0.012                                                                           & 2.083                                      & 1.532-2.834                                & 2.119                                      & 1.551-2.895                                &                                          \\ %\checkmark

@@

NDFIP1                                         & Nedd4 family interacting protein 1                         & \num{2.6e-6}                               & 0.017                                                                           & 2.031                                      & 1.502-2.746                                & 2.027                                      & 1.483-2.771                                &                                           \\ %\checkmark 

@@

FOXA2                                          & forkhead box A2                                            & \num{2.7e-6}                               & 0.018                                                                           & 1.976                                      & 1.479-2.640                                & 1.914                                      & 1.426-2.569                                &                                         \\ %\checkmark  

@@

\multicolumn{9}{|l!{\color{black}\vrule}}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~~\\~Kaplan-Meier Bonferroni-adjusted \textit{P} $< 0.05 $~\\~Cox's univariate and multivariate$ HR > 1.5$ \end{tabular}}                                                                                                                                                                                                                                                              \\ 

@@

%\multicolumn{9}{|l!{\color{black}\vrule}}{Remark: \checkmark validated by GSE2837}                i                                                                                                                                                                                                                                                                                                                                             \\

@@

} % resizebox end

@@

\caption{The other top 10 genes overexpressed with better prognosis in \acrshort{hnscc} (ranked by adjusted \textit{P} value) }

@@

ZNF557                                         & zinc finger protein 557                                & \multicolumn{1}{l!{\color{black}\vrule}}{\num{8.6e-8}} & \multicolumn{1}{l!{\color{black}\vrule}}{0.001}                                                      & \multicolumn{1}{l!{\color{black}\vrule}}{0.465} & \multicolumn{1}{l!{\color{black}\vrule}}{0.348-0.619} & \multicolumn{1}{l!{\color{black}\vrule}}{0.499} & \multicolumn{1}{l!{\color{black}\vrule}}{0.372-0.669} &                                              \\ 

@@

ZNF266                                         & zinc finger protein 266                                & \num{2.2e-7}                                           & 0.001                                                                                                & 0.474                                           & 0.355-0.632                                           & 0.453                                           & 0.338-0.607                                           &                                              \\ 

@@

IL19                                           & interleukin 19                                         & \num{3.7e-7}               & 0.002                                                                                                & 0.472                                           & 0.351-0.635                                           & 0.459                                           & 0.340-0.619                                           &                                             \\ %\checkmark

@@

MYO1H                                          & myosin 1H                                              & \num{3.8e-7}               & 0.003                                                                                                & 0.468                                           & 0.347-0.632                                           & 0.467                                           & 0.344-0.634                                           &                                              \\ 

@@

FCGBP                                          & Fc fragment of IgG binding protein                     & \num{1.2e-6}               & 0.008                                                                                                & 0.484                                           & 0.359-0.653                                           & 0.496                                           & 0.366-0.674                                           &                                             \\ %\checkmark

@@

%LOC148709                                      & LncRNA LOC148709                                       & \textcolor[rgb]{0,0,0.471}{\num{1.5e-6}}                                           & 0.010                                                                                                & 0.499                                           & 0.374-0.666                                           & 0.485                                           & 0.361-0.652                                           &                                              \\ 
EVPLL                                          & envoplakin-like protein                                & \num{2.0e-6}                                           & 0.013                                                                                                & 0.490                                           & 0.363-0.661                                           & 0.494                                           & 0.364-0.672                                           &                                              \\ 

@@

PNMA5                                          & paraneoplastic antigen like 5                          & \num{2.6e-6}                                           & 0.017                                                                                                & 0.499                                           & 0.371-0.671                                           & 0.481                                           & 0.357-0.650                                           &                                              \\ 

@@

IQCN                           & \num{3.1e-6}                                           & 0.020                                                                                                & 0.500                                           & 0.371-0.673                                           & 0.483                                           & 0.356-0.654                                           &                                              \\ %\checkmark

@@

NPB                                            & neuropeptide B                                         & \num{4.0e-6}                                           & 0.027                                                                                                & 0.460                                           & 0.328-0.646                                           & 0.457                                           & 0.324-0.646                                           &                                              \\ %\checkmark

@@

CALML5 &
\acrlong{CALML5} &
   \num{2.0e-4} & %\num{6.54e-6} & %3.7e-7} &
   0.039 &
   0.510 &
   0.379-0.686 &
   0.493 &
   0.364-0.667 &  \\  % \checkmark \multicolumn{2}{l|} {

@@

\multicolumn{9}{|l|}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~\\~Kaplan-Meier Bonferroni-adjusted \textit{P} value \textless{} 0.05~\\~Cox's univariate and multivariate HR \textless{} 0.6\\

@@

%lncRNA: Long non-coding RNA\\%Remark: \checkmark Validated by GSE2837

@@

\section{SFigures}
%\underline{Supplementary figure legends}\\[1cm]
%S1
Supplementary figure \ref{fig:pvaluePlot_NDFIP1}:\\
The gene NDFIP1, one of our 20 preliminary candidates, has a \textit{P} value (around $0.05$) at 50\% quantile cutoff, achieving a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff.% (please see supplementary Figure S1).
After the FDR correction, NDFIP1 still has \textit{P} value of \num[round-precision=3, round-mode=figures,
scientific-notation=true]{0.0001074233}.
However, NDFIP1 could not pass the validation by using GSE65858 cohort.

@@

%%%%%
% S1
% supplementary figure
\begin{figure}[ht]
    \centering
    \includegraphics[width=10cm]{Rplot_pvaluePlot_NDFIP1.pdf}
    \caption{Under cutoff-finding procedure of Kaplan-Meier analysis, the \textit{P}-value plot of gene "NDFIP1" shows: (1) 70\% of \textit{P} values is $<0.05$; (2) the median-cut zone (zoom-in and revealed in inset box) has a "W"-like distribution; (3) sliding-window cutoff selection could find it's optimized \textit{P} values (far less than 0.001) while a median cut might yield \textit{P} value $>=0.05$.\\
    (x-axis: grouping by person number; y-axis: \textit{P} value in log10 transformed)}
    \label{fig:pvaluePlot_NDFIP1}
\end{figure}

@@
